\chapter{Development Methodology}
This section contains descriptions regarding the different development
methodolo- gies that have been brought up and that have been researched. Each subsection
includes both a short explanation, advantages and drawbacks for each methodol-
ogy.

\subsection{The Waterfall Method}
Figure x.x shows a graphical explanation of the sequential design process called the waterfall method. This method has been around for decades. The waterfall method is based on the idea of visiting each of the phases, Initiation, Analysis, Design, Construction, Testing, Implementation and Maintenance, only once and finish one before starting the next. The name is given from the idea of progress flowing through each face, like a waterfall. This results in huge challenges regarding controlling dependencies if the project doeas reiteration over previous phases at a later stage.

The main advantage to the waterfall method is that bugs and changes are cheaper to fix if you fix them right away, as it will save you a lot of time/money later on.
The main drawbacks are as mentioned earlier, that once the project has moved on to the next phase and the team should not backtrack and edit the previously completed phases, since this might make the further implementation more difficult. The fact that planning has to be done very thoroughly in the beginning to avoid having to reiterate previous phases at a later stage as this can be costly and completed, is also a disadvantage. Leading to a problem with projects where there is no overview to what is to be done and how long time it will take, this method will lead to uncertainty. A roll back to an earlier stage will most likely prove early estimates wrong and might cause complications to the development.

\subsection{Scrum}
\label{sec:scrum}
Figure x.x shows a graphical explanation of the Scrum method, one of many agile development methods. Agile development meaning that it is an iterative, incremental model which emphasizes on doing several short sprints where the goal is to complete some smaller set of tasks. After a given period, usually one to four weeks, the development team summarizes what have been done and what is left from the current sprint, needing to be completed in the upcoming sprints.
The advantages of scrum are that it makes the software development more versatile, the team can work on all phases and parts of the project at the same time, and update earlier assumptions based on newer discoveries. Meaning that requirements and modelling does need to be finished before starting implementation and because of this, changes are less expensive to do. This is done by having a more relaxed relationship to documentation of source code and the process.
Nothing is written in stone until the product is done, as opposed to the waterfall method, mentioned earlier.
The main drawback of Scrum is the complexity of it. All methods has a certain learning curve at the beginning, leading to stress or less effective work. Scrum has several submethods, all with small differences. This may lead to a learning curve for experienced users.
A more specific explanation of how this project used Scrum is found in Section x.x

\subsection{Choice of methodology}
The development chose the Scrum methodology instead of the Waterfall method, due to many reasons. Foremost, the customer asked the team to work in the Scrum methodology. "We want the process to be as agile as possible, to a certain level. Waterfall will not suffice". The customer had many ideas regarding the layout and the functionality of the applications, and were not sure what to include. This leading to a situation where spending time making a detailed requirement specification and locking down all the details was pointless.
The customer was likely to make changes to the initial requirements once the first plan was ready. Secondly, the team was way more eager to try out scrum than to use waterfall. The simple fact that scrum is highly recommended by real-life developers, is a good argument for doing so. The developers were also eager to learn more about Scrum, as not all had used it before.


\input{DevelopmentMethodology/Sprints}
