\section{Customer Information}
\label{sec:custinf}
The customer of this project is "Sykehusapotekene i Midt-Norge". 

\subsection{Sponsor}
The sponsor of this project is Extrastiftelsen.

\subsection{Partners}
The Norwegian University of Technology and Science are partner in this project. Norges Astma og Allergiforbund (NAAF) has also been included in the work, both for feedback and helpful information. Table \ref{tab:customercontacts} shows relevant contacts for the customer. 

\subsection{Customer contacts}
Table \ref{tab:customercontacts} gives an overview of the contact information for the customers.
\begin{table}
	\begin{center}
		\begin{tabular}{|p{4cm}|p{7cm}|}   
			\hline      
			\bf{Name} & \bf{Email} \\ 
			\hline
			Ole Andreas Alsos & \href{mailto:oleanda@idi.ntnu.no}{oleanda@idi.ntnu.no}  \\     
			\hline
			Elin Høien & \href{mailto:elin@hoien.no}{elin@hoien.no}
			\\
			\hline
			Marikken Høiseth &
			\href{mailto:marikken.hoiseth@ntnu.no}{marikken.hoiseth@ntnu.no}\\
			\hline
			Hanne Linander &
			\href{mailto:hanne.linander@gmail.com}{hanne.linander@gmail.com}
			\\
			\hline
		 \end{tabular}
	\end{center}
	\caption{Customer contacts}
	\label{tab:customercontacts}
\end{table}
\clearpage{}
%Vi bør ta enten tabell, eller project group her. Tabellen må da selvsagt utvides.
\subsubsection{Project Group}
\begin{itemize}
  	\item Cand Pharm Elin Bergene, Sykehusapotekene i Midt-Norge (Hospital pharmacies in Central Norway)
	\item PhD Ole Andreas Alsos, Norsk Senter for Elektronisk Pasientjournal (NSEP) (Norwegian Center for Electronic Patient Journal) and Institute for Computer Science (IDI), NTNU (Ph.D as of 2011). Ole is also working part time at BEKK Consulting. 
	\item Scholarship Marikken Høiseth, Institute for Product Design (IPD), NTNU.
	\item Bo Alexander Gleditsch, communication advisor NAAF.
	\item Rose Lyngra, senior advisor NAAF.
\end{itemize}

\subsubsection{Affiliates}
The project is in close collaboration with the following affiliates:
\begin{itemize}
  	\item Sykehusapotekene i Midt-Norge (SHAP) will be a test arena for the result of the project. They will work further with the results.
	\item Norsk Senter for Elektronisk Pasientjournal (NSEP). NTNUs activities within health informatics is gathered at NSEP. The project will take advantage of 
the academic community and the infrastructure at NSEP (offices and usability lab).
	\item Department for product design (IPD) at NTNU will consult upon design. 
	\item Department for computer and information science arranges the course and will provide an advisor for the group, Tobias B. Iversen. 
	\item Norges Astma og AllergiForbund (NAAF). The project has been created by NAAF. NAAF will provide expertise about the user groups of the final applications. NAAF will work further with the results of the project. 
\end{itemize}

\subsubsection{Stakeholders}
A stakeholder is a person, group or an organization that has interest in a project. The
different stakeholders of this project are listed in Table \ref{tab:stakeholders}. This table also contains
a short rationale for why each party has been listed, and what their main
concerns for the applications are.

\begin{table}
	\begin{center}
		\begin{tabular}{|p{0.3\linewidth}|p{0.6\linewidth}|}   
			\hline      
			\bf{Stakeholder} & \bf{Rationale} \\ 
			\hline
			NAAF & Wants to see whether this is a possible solution to make it easier for children to take their medicine. Also interested in proof-of-concept.
			\\
			\hline
			Sykehusapotekene i Midt-Norge & Cooperates with NAAF to find out if there is an easier
			way to make children take their medicine. 
			\\
			\hline
			Developers & Wants the applications to be a success, as it is their work. The level of success also affects the degree in one of their courses.
			\\
			\hline
			NTNU & Wants the project to be a success to front the research that is done by
			the university.
			\\
			\hline
			Children diagnosed with asthma & Needs something to make it easier to go through
			with each treatment.
			\\
			\hline
			Parents of children diagnosed with asthma & Needs instructions on how to use
			medicines correctly. Needs reminders about when to give their children their medicines. Needs an
			organized way to see what medicines have been taken earlier. Wants their children to
			suffer less during medication, and be happier about taking their medicine.
			\\
			\hline 
			Extrastiftelsen & Main funder of the project. 
			\\
			\hline
		\end{tabular}
	\end{center}
	\caption{Stakeholders}
	\label{tab:stakeholders}
\end{table}