\section{Responsibilities among roles}

In the following section all roles and their responsibilities are explained.

\subsubsection{Test Master}
The test master is responsible for developing a test plan, initiate testing 
and follow up on test results. The test master will have the last vote in 
whether a test is passed or not. The test master will be responsible for all 
parts of testing, including unit testing, integration testing, and system 
testing, however, the customer will be responsible for acceptance testing.

\subsubsection{Scrum Master}
Scrum master is accountable for removing impediments to the ability of the team 
to deliver the sprint goal. The scrum master is no team leader, but is a kind 
of buffer between the development team and distracting influences. The scrum master 
is the enforcer of rules and responsible for ensuring that the scrum process is 
used as intended.

\subsubsection{Customer contact}
The customer contact is responsible of all contact with the customer outside 
of the customer meetings. Including sending meeting invitations, clarifying 
questions outside of customer meetings and other inquiries to the customer. 
Customer contact works as a single-point two-way communicator, to reduce 
amount of communication points. 

\subsubsection{Advisor contact}
The advisor contact is responsible of all contact with the advisor outside 
of the advisor meetings. Including sending meeting invitations, clarifying 
questions outside of advisor meetings and other inquiries to the advisor. Advisor 
contact works as a single-point two-way communicator, to reduce amount of 
communication points.

\subsubsection{Document Owner}
The Document owner is responsible of finding a suitable tool for writing the report in LaTeX. The document owner is also responsible for making sure all the correct document is added to the report, and will let the group know if something is missing. 

\subsubsection{Meeting report master}
Meeting report master is responsible for taking notes during all internal, 
customer and advisor meetings. Meeting reports should meet a specific standard, 
given by the project compendium. It is the responsibility of the meeting 
report master to ensure this standard is enforced.

\subsubsection{Backend developer}
More than one person may have this role. Backend developer(s) are responsible 
for developing the backend parts of the applications. Including: 

\subsubsection{GUI developer}
More than one person may have this role. GUI developer(s) are responsible for 
developing the graphical user interface of the applications. Inluding layout, 
graphics, color scheme, etc. 

\subsubsection{Karotz programmer}
The the robot-Bunny, named Karotz, has an API for implementing features for controlling the robot to an application. These functionalites are such as changing the color of an LED light on the robot's stomach, waving it's ears and playing mp3-files, among many more.
The Karotz programmer is responsible for developing this specific part of the application. 

\subsubsection{Database manager}
The database manager is responsible for selecting a suitable database tool for 
the applications. The role also includes the responsibility of managing the 
database architecture and connections to the database.

\subsubsection{System architect}
The system architect is responsible of the overall architecture of the source code. 
The architect has final vote in decisions regarding architecture specific problems. 
