\chapter{Prestudy}
\label{chap:prestudy}
\section{Children with asthma}
Asthma is a chronic lung disease that alot of people suffer from. It is often more prominent in children, who are more active and easily exited then
adults. The asthma is typically triggered by exitement, physical activity, rashes or allergies. The problem is managed by multiple medicines, 
with different schedules as to when to take them depending on the condition of the child. There are inhalation medicines that consists of either 
small dustparticles that effect the lungs locally, or saltwater that are inhaled as vapor, either alone or combined with other medicines to loosen 
up slime. There are also pills or liquid medicines that either affects the immune system or affects the body globally, not just locally in the lungs.

The medicines can also be divided into medicines that have immidiate effects, and are used during an asthma attack, while other medicines are preventive, 
and is taken on a regular schedule. In addition you have preventitive medicines targeted at bolstering your immune system before going to areas or days
where the child is likely to be in contact with materials it is alergic to.	

With some of the inhalationmedicines it's difficult to time the inhalation with the release of medicine, and here an inhalation chamber, or inhalation 
mask, is used. When the child has taken the nebulizer this way, that is usually taken once or twice a day, they must remember to wash their mouth. 

\section{Parents with children affected by asthma}

Parents of children with asthma face a series of challenges concerning the medicination of their children. 
One of these challenges is to give the correct amount of medicine, the right type of medicine, at the 
correct time of the day. Many parents have experienced stressful mornings where they are late for work, 
their children is unwilling to take their medicine and they either do it in an incorrect way, reducing the 
medicines effect, or not at all. The medication plans can be hard to understand, even though they are 
designed to be easy, and it's typically only one of the parents that have gotten the instructions from 
the doctor directly, and it becomes even harder for the other one to do it correctly.

The children isn't always happy about taking their medicine. The inhalation mask might be scary, the 
medication might interfere with their planned activities that day, or any number of other reasons the child 
might not want to take his medicine that day. Having to force a child to take their medicine could make the 
child associate taking the medicine with a negative experience, and it becomes increasingly difficult to 
give the medicine to the child. 

\section{The concept of gamification}

Gamification is the concept of applying game-design thinking to non-game applications to make them more fun and engaging. The term
was first mentioned in March 2004, but was not popular before 2010. By using gamification, we hope to make asthma treatments for children
more enjoyable to do.


There exists a lot of common techniques applied to introduce gamification to a process. These techniques include, but are not limited to:
\begin{itemize}
  \item Achievements/badges
  \item Levels
  \item Leaderboards
  \item Progress bars
  \item Avatars
  \item Gifting
  \item Challenges
  \item Embedding of minigames
\end{itemize}

These techniques are all widely used. Here are some examples:
\begin{itemize}
  \item Games for PlayStation and XBOX are more used online now, and fewer people are playing thos game offline.
   To make people finish the campaign the these games, they are using trophys to motivate people to complete games 100\%. 
   You may have to collect every single item in the game, fight every boss and so on.
  \item Nike+ introduced gamification to training. You can track how fast you run, your maximum pulse and so on, and try to beat this target the next time you are running.
  \item You ``check in'' to places you have been with Google Maps.  
  \item Airline companies uses points as bait for customers to fly more with a company. At a certain level of these points, you may get one more flight for free, get a free upgrade to a better seat
  and so on. 
\end{itemize} 

%Kanskje skrive om dette?
As previously mentioned, we hope gamification will help making children's treatment as enjoyable as possible. Michael Wu (Ph.D in Biophysics) has proven that gamification has an impact on human motivation. 
As Michael Wu presents it:
``Game mechanics and game dynamics are able to positively influence human behavior because they are designed to drive the players above the
activation threshold (i.e. the upper right of the ability-motivation axis), 
and then trigger them into specific actions'' (Wu, 2011).  
Game mechanics have been proven to positively influence human behaviour, because these game mechanics are designed to drive the players ab
%Referanser: gamification.org, Gamification 101 (se bibliografi)


Even though gamification has a lot of positive sides, it has a bad side if gamification is done the wrong way.
The fact that we are using gamification to motivate children, it makes it even worse. If children feels that
they are stuck in a game, motivation may very easily be broken down. So whatever concept we come up with, it has to be 
to motivate the children at all time. They cannot feel stuck with our concept. This concept is up to the customer to create, 
while we will be implementing it.  

\input{Prestudy/Karotz}



 
