\section{Description of the User Group}
\label{descriptionoftheusergroups}

The use cases and requirements in the following chapter will deal with three different user groups; the patient, the next-of-kin and the medical staff. In this section we describe what characteristics these user groups have, and how they are assumed to interact with the applications.

\subsection{The Patient}
The patient user group is a diverse group of children suffering from asthma. Patients are for the most part under ten years of age, have a short attention span and are likely to have little experience with technology. It is assumed that each patient is being helped by their next-of-kin in order to understand the applications.
In addition to the abilities mentioned, small children are as diverse as any other group of people. Meaning that they can be very healthy and competent except for their illness. Some children understand technology easier than others and it mostly based on their evolution of perception. Small children are more often easily scared, so the applications should not include sudden animations or scary characters.
Since it is expected that next-of-kin will help the children with these applications, this user group is not the main focus. 

\subsection{Medical Staff}
The medical staff is a group of doctors, nurses and apothecaries that prescribes the asthma medicine and gives the children other regular medicine, typically a nebulizer, that makes alot of sound and gives of smoke, scaring the children. It is paramount to the success of the medication that the medical staff can properly describe to the next-of-kin and children how to correctly take the medicine. It may also be helpful for the next-of-kin to have a reference or manual describing how to take the medicine, so they can review it.

\subsection{Next-of-kin}
Next-of-kin is the person responsible for the children on a daily basis. This person will be the link between the hospital and the patient. 
Typically the next-of-kin have a tighter schedule than the patient and require help to quickly and effortlessly give daily and otherwise necessary medicines, that the patient might be reluctant to take, due to the medicines being boring and possibly scary. It is also important that the next-of-kin is motivated to keep the medicationplan laid out by the medical staff, and that they give the patient the medication in a timely and correct fashion.