\chapter{Further Work}
\label{chap:Further Work}

This chapter gives an overview of some of the ideas both the customer and the developers had for further development of the application. This includes a description of further development, analysis of the user groups and work towards NAAF and the health department.
The main part of the work to be done after the end of this project is connected to requirements that has been taken out of this project due to limitation of time and resources. Other issues remaining is connected to the security and privacy of the patient's treatment log and storing sensitive information.
Section X.XX lists the overall requirements that have not been implemented during the project. These requirements has either been requested early in the process of have been brought up during discussions and meetings with the stakeholders. 

% Here goes the major potential improvements such as privacy/security, rewardsystem and connection
\section{Improvements}


\input{FurtherWork/WebAccess}
\input{FurtherWork/SecurityAndPrivacy}


\subsection{Rewardsystem}The childrens application (CAPP) are all about changing the childrens view of medication to something positive. It shall be a motivation for the children to take their medication. It is therefore an important task to entertain them and give them some form of reward when they take their medication. As for now, we have given stars to the child after taken medication. This stars are in a treasure chest where the child can see how many stars it has. This is an easy reward and worked fairly well under the user tests. However, it may be boring over time. The initial idea was to have a shop where the children could buy clothes and stuff to their avatar. This was not implemented due to time concerns. There are also possible to take this to the real world. E.g. that the child gets a lollipop for evrey 10th star.  There are a endless line of opportunities for this reward system, and we chose the easiest part to have something to test. Hanne, who writes a thesis about this project has developed a potential evlolvement of this reward system. This includes an interactive storyline where the story evolves based on the childs choices. More on this in her report \ref{XXX}. 

\subsection{User testing of the guardian application}The GAPP has not yet been user tested on actual parents of asthmatic children. This has to be done to get an understanding of how they interact with the system, and to get knowledge about what they think of an application of this type. This is a system to make it easier for the guardians to give their children medications. It doesn't matter what the children thinks if the guardians only think this would slow down the process, because the system will never be used if the guardians don't like it.% Here goes the minor ideas and improvements for further work
\section{Further ideas and minor improvements}


\begin{description}

\item[Webinterface] The doctors may prefer to set up the users medication plans through a webinterface on their computers. 

\item[Other devices] The application are fitted for a phone running the Android operating system. For the future it should also be scalable to tablets. There may be more interesting for a child to work on a tablet than a phone. There will also be much more space for content. This extra space gives greater potential of the reward system. It should also be available on other operating systems than Android, e.g. iOS or Windows Phone. This will improve the availiability for the users, not limiting them to Android phones. 

\item[Overall graphical design] The priorities have been to make the major functionality work. We have used lots of time making the applications understandable and easy to use, but there is still a great potential in making the applications interaction design better. 

\item[Personalize the system] The application may be more personalized. E.g. "It's time to take medication" could be "It's time to take medication, Eric". By involving the users name more in the system, they may feel more appreciated. 

\end{description}