\chapter{Usability Testing}
\label{sec:Usabilitytesting}
This section will explain what usability testing is, and what we did during our project relating to usability testing.

\section{What is usability testing}
Usability testing is a way to test your system on users, using the interaction design of the system. Usually this entails setting up 
a few tasks for a user, giving the user access to the system and seeing how well the user is able to solve the tasks given in the test
with the system provided. The usability testing focuses on the main functionality rather than on the details. 

\section{How to do usability testing}
The test usually starts with the tester explaining for the user the different parts of the systems being used, and that it's the system being
tested, not the user. The tester also explains that this means the user can't do anything wrong, if there is something the user doesn't 
understand, that is fine. The tester observe what the user finds hard, or can't do at all, and notes this down as things that might have
to be changed on the system. 

At last, the user is given an evaluation form of the system, typically a SUS-form (System Usability Scale), and time to talk about
how well they felt the system helped them solve the tasks given. %Add reference to SUS?

\section{Usability testing in our project}
Our project largely implements user interraction, and usability testing plays a key role in getting a good result, since so much
of the project is centered around the user interface. We started the project with an early paper prototype test, to get some feedback on the ideas
we got after the workshop we did with the interaction design group. After this we worked for some time on implementing the system, before we late in
the project did a full usability test using the hallway method, testing our system on children to see if it helped them take their medicine, and seeing
if there was some bugs or things we could implement better.

\input{Testing/paperprototypetest}

\input{Testing/usabilitytestonchildren}