\section{Quality Assurance}
\label{sec:qualityAssurance}
\subsection{Language}
As a main language for the development project, Norwegian was chosen. 
The decision was due to all members, customer contacts and the advisor 
being Norwegian. The report is written in English. All code, including comments were all in English. The language in the applications was chosen
to be Norwegian, since the applications is targeted towards norwegian 
children who do not necessarily understand English.

\subsection{Customer Meeting}
Customer meetings were held once a week. The reason behind this schedule 
was due to the customers desire of high involvement in the project, and 
the belief that having a high frequency of meetings would result in a higher 
quality result. High involvement makes the process of feedback and new ideas 
easier, and restricts the possibilities for the development team tracking 
off course. The meetings were usually held on Mondays. If any unexpected 
events resulted in meetings being moved, a notice where given at least 24 hours in advance. 
The first customer meeting was held at St. Olavs Hospital the 21st of August. 

\subsection{Advisor Meeting}
%TODO update references
The advisor meeting were held each Monday at Campus Gl\o shaugen. See Appendix \ref{apx:templates} 
for a typical meeting agenda. The main items of the agenda was the meeting approval of the report from the last 
meeting, a project status report and discussion on problems and difficulties. 
A plan for the following week was also presented. During the meetings, the 
advisor was able give feedback on the status of the report regarding the 
quality expected from the final result. 


