\blankpage{}
%\chapter{Bibliography}
\begin{thebibliography}{00}
\label{sec:Bibliography}
\bibitem{scrummodel}{\emph{Scrum process.svg}. October 07 2012. Available at:
	{\tt <}\href{http://www.wikipedia.org/}{www.wikipedia.org}{\tt >}}
\bibitem{waterfallmodel}{\emph{Waterfall Model}. October 07 2012. Available at:
	{\tt <}\href{http://compsci.ca/}{compsci.ca}{\tt >}}
\bibitem{ventoline}{\emph{Riktig bruk av inhalatorar}. November 17 2012. Used with permission. Sjukehusapoteka Vest. Available at:
	{\tt <}\href{http://sjukehusapoteka-vest.no}{www.sjukehusapoteka-vest.no}{\tt >}}
\bibitem{freqflyer}{\emph{Frequent Flyer Programs}. November 10 2012. Gamification Wiki. Available at:
	{\tt <}\href{http://www.gamification.org/}{www.gamification.org}{\tt >}}
\bibitem{gamificationByDesign}{Zichermann G, Cunningham C (2011). \emph{Gamification By Design}. O'Reilly Media, Inc. ISBN: 978-1-4493-9767-8}
\bibitem{trophies}{Hamari J, Eranti V (2011). \emph{Framework for Designing and Evaluating Game Achievements}. Proceedings of DiGRA 2011 Conference: Think Design Play.}
\bibitem{naafastma}{\emph{Fakta om astma}. Published 10.01.2006. Available at:
	{\tt <}\href{http://www.naaf.no/}{www.naaf.no}{\tt >}}
\bibitem{naafasthma}{\emph{Useful facts on pollen allergy (pollenallergi)}. Published 22.04.2007. Available at:
	{\tt <}\href{http://www.naaf.no/}{www.naaf.no}{\tt >}}
\bibitem{swot}{Jackson S, Joshi A, Erhardt N (2003). \emph{Recent Research on Team and ORganizational Diversity: SWOT Analysis and Implications}. Journal of Management 2003}
\bibitem{waterfall}{Royce W (1970). \emph{Managing the Development of Large Software Systems}. Proceedings IEEE WECSON 26}
\bibitem{agilemanifesto}{Beck K, Beedle M, van Bennekum A, Cockburn A, Cunningham W, Fowler M, Grenning J, Highsmith J, Hunt A, Jeffries R, Kern J, Marick B, Martin C, Mellor S, Schwaber K, Sutherland J, Thomas D (2001). \emph{Agile Manifesto}. Available at: 
	{\tt <}\href{http://agilemanifesto.org/}{agilemanifesto.org}{\tt >}}
\bibitem{androidservice}{\emph{Android API Reference: Service class}. November 13 2012. Available at:
	{\tt <}\href{http://developer.android.com/}{developer.android.com}{\tt >}}
\bibitem{mysqlmarketshare}{\emph{MySQL Marketshare}. September 20 2012. Available at:
	{\tt <}\href{http://www.mysql.com}{www.mysql.com}{\tt >}}
\bibitem{gamification101}{Wu M (2011). \emph{Gamification 101: The Psychology of Motivation}. Lithioshphere's Building Community blog. Available at:
	{\tt <}\href{http://lithosphere.lithium.com/}{lithosphere.lithium.com}{\tt >}}
\bibitem{karotz}{\emph{Karotz}. October 09 2012. Available at:
	{\tt <}\href{http://www.karotz.com/}{www.karotz.com}{\tt >}}
\bibitem{pellingblog}{Pelling N (2011). \emph{The (short) prehistory of ``gamification''\ldots}. Nick Pelling's personal blog at Wordpress. Available at:
	{\tt <}\href{http://nanodome.wordpress.com}{nanodome.wordpress.com}{\tt >}}
\bibitem{danielsblog}{Daniels M (2011). \emph{Businesses need to get in the game}. Marketing Week. Available at:
	{\tt <}\href{http://www.marketingweek.co.uk}{www.marketingweek.co.uk}{\tt >}}
\bibitem{nodejs}{\emph{About NodeJS.} October 10 2012. Available at:
	{\tt <}\href{http://nodejs.org/about/}{nodejs.org}{\tt >}}
\bibitem{bassclemetskazman}{Bass L, Clements P, Kazman R (2003). \emph{Software Architecture in Practice, 2nd Edition}}
\bibitem{php}{\emph{About PHP.} October 13 2012. Available at:
	{\tt <}\href{http://www.php.net/}{www.php.net}{\tt >}}
\bibitem{javadoc}{\emph{javadoc - The Java API Documentation Generator}. November 13 2012. Oracle. Available at
	{\tt <}\href{http://docs.oracle.com/}{docs.oracle.com}{\tt >}}
\bibitem{andersonrainie}{Anderson J, Rainie L (2012). \emph{Gamification: Experts expect `game layers' to expand in the future, with positive and negative results}. Pew Research Facility.}
\bibitem{dropbox}{\emph{About Dropbox.} September 12 2012. Available at:
	{\tt <}\href{http://www.dropbox.com/}{www.dropbox.com}{\tt >}}
\bibitem{agilezen}{\emph{What is AgileZen?} August 30 2012. Available at:
	{\tt <}\href{http://www.agilezen.com/}{www.agilezen.com}{\tt >}}
\bibitem{helsebibastma}{R\o{}d G, \O{}ynar K, Skadberg B (2006, rev. 2009). \emph{Astma Bronkiale}. Helsebiblioteket.no. Available at:
	{\tt <}\href{http://bit.ly/T1f2Dl}{bit.ly/T1f2Dl}{\tt >}}
\bibitem{conundraltd}{\emph{Conundra Ltd}. October 20 2012. Available at:
	{\tt <}\href{http://www.nanodome.com/conundra.co.uk}{www.nanodome.com/conundra.co.uk}{\tt >}}
\bibitem{mysql}{\emph{MySQL}. November 03 2012. Available at:
	{\tt <}\href{http://www.mysql.com/why-mysql}{www.mysql.com/why-mysql}{\tt >}}
\bibitem{nebulizer}{\emph{IH25}. November 12 2012. Used with permission. Available at:
	{\tt <}\href{http://www.beuler.com/}{www.beuler.com}{\tt >}}
\bibitem{androidguidelines}{\emph{Design Principles}. October 02 2012. Available at:
	{\tt <}\href{http://developer.android.com}{developer.android.com}{\tt >}}
\bibitem{diskrimineringsloven}{\emph{Om lov om forbud mot diskriminering på grunn av nedsatt funksjonsevne (diskriminerings- og tilgjengelighetsloven)}. November 09 2012. Available at:
	{\tt <}\href{http://bit.ly/UzZloH}{bit.ly/UzZloH}{\tt >}}
\bibitem{json}{\emph{About JSON}. November 05 2012. Available at:
	{\tt <}\href{http://www.json.org}{www.json.org}{\tt >}}
\bibitem{balsamiqmockups}{\emph{Balsamiq Mockups}. September 07 2012. Available at:
	{\tt <}\href{http://www.balsamiq.com}{www.balsamiq.com}{\tt >}}
\bibitem{personalinformation}{\emph{Personal information and data protection}. November 13 2012. Available at:
	{\tt <}\href{http://www.datatilsynet.no}{www.datatilsynet.no}{\tt >}}
\bibitem{postman}{\emph{POSTMan}. November 06 2012. Available at:
	{\tt <}\href{http://github.com/a85/POSTMan-Chrome-Extension}{github.com/a85/POSTMan-Chrome-Extension}{\tt >}}
\bibitem{4+1viewmodel}{Krutchen P, 1995. \emph{Architectural Blueprints---The ``4+1'' View Model of Software Architecture}. IEEE Software}
\bibitem{calendarview}{Gao C, 2011. \emph{CalendarView}. Available at:
	{\tt <}\href{http://code.google.com/p/android-calendar-view}{code.google.com/p/android-calendar-view}{\tt >}}
\bibitem{ntnuphpmyadmin}{\emph{MySQL on IDI}. November 06 2012. Available at:
	{\tt <}\href{http://drift.idi.ntnu.no}{drift.idi.ntnu.no}{\tt >}}
\bibitem{livingwithasthma}{Borge C, Engh N, Austegard E, Sandsund C, Hamre H, Slettedal I, Alam H, Erikstad T (2002). \emph{How to live with asthma}. Norges astma- og allergiforbund.}
\bibitem{Kanban}{Anderson D, 2003. \emph{Agile Management for Software Engineering: Applying the Theory of Constraints for Business Results.} Prentice Hall.}
\bibitem{jodatime}{ \emph{About Joda Time }. November 10 2012. Available at: {\tt <}\href{http://joda-time.sourceforge.net/}{joda-time.sourceforge.net}{\tt >}}
\bibitem{AndroidSDK}{ \emph{About Android SDK}. November 14 2012. Available at: {\tt <} \href{http://developer.android.com/}{developer.android.com}{\tt >}}
\bibitem{AndroidADT}{\emph{About Android Developer Tools}. November 14 2012. Available at: { \tt <} \href{http://developer.android.com/}{developer.android.com}{\tt >}}
\bibitem{Eclipse}{\emph{About Eclipse IDE}. November 14 2012. Available at: {\tt <} \href{http://www.eclipse.org/}{www.eclipse.org}{\tt >}}
\bibitem{TIOBE}{\emph{TIOBE Programming Community Index for November 2012}. November 15 2012. Available at: {\tt <} \href{http://www.tiobe.com/}{www.tiobe.com}{\tt >}}
\bibitem{git}{\emph{Git source code management} Available at: {\tt <} \href{http://git-scm.com/}{git-scm.com}{\tt >}}
\end{thebibliography}