\chapter{Project Management}
\label{chap:projectManagement}

\input{ProjectManagement/Members}

%\input{ProjectOrganization/Qualities}

\section{Roles}
Early in the planning phase, on August 24th 2012, the group held a meeting to distribute
team roles for the project. We discussed which parts were needed for a system fitting the description,
and we decided on four main parts: GUI, back-end, database and Karotz. In addition, proper development
requires testing so we saw the need for a person in charge of testing, and a person in charge of
general quality assurance. We also needed a high-level system architect who could keep the
project well-structured and easily maintainable, especially considering that the system spans over
at least three different subsystems (database, Karotz and Android applications). Since the group was to keep
close contact with both the customer and the group advisor, responsibilities were assigned to these
roles as well. There would also be a need to write reports for meetings with these third parties, so
a secretary was necessary. At last, the group had already decided to use an agile 
development model, so a person in charge of this was needed as well (``Scrum master").

We have identified the following roles for the project. 
\begin{itemize}
\item Test Master - Eirik
\item Scrum Master - Aleksander
\item Customer Contact - Aleksander
\item Advisor Contact - Esben
\item Document Owner - Yngve
\item Secretary - Jørgen
\item Karotz Developer - Yngve
\item Database Manager - Yngve
\item System Architect - Esben
\item Quality Assurance manager - Jørgen 
\end{itemize}


\input{ProjectManagement/ResponsibilitiesAmongRoles}

\section{Weekly schedule}

The development team had the following fixed weekly schedule:

\begin{itemize}
\item Customer meeting: Monday 12:15-13:00
\item Advisor meeting: Monday 13:15-14:00
\end{itemize}
Rooms were reserved on demand. There were also at least one day a week were the development team works together in the same room. 

\input{ProjectManagement/Workplan/Workplan}
\input{ProjectManagement/RiskAnalysis}
\input{ProjectManagement/QualityAssurance/QualityAssurance}