\section{Responsibilities among roles}

In the following section all roles and their responsibilities are explained.

\begin{description}
	\item[Test Master] The test master is responsible for developing a test plan, initiate testing 
		and follow up on test results. The test master will have the last vote in 
		whether a test is passed or not. The test master will be responsible for making sure all 
		parts of testing is done, including unit testing, integration testing, system 
		testing and acceptance testing with the customer.
	
	\item[Scrum Master] Scrum master is accountable for removing impediments to the ability of the team 
		to deliver the sprint goal. The scrum master is no team leader, but is a kind 
		of buffer between the development team and distracting influences. The scrum master 
		is responsible for ensuring that the scrum process is 
		used as intended.

	\item[Customer Contact] The customer contact is responsible of all contact with the customer outside 
		of the customer meetings. This includes sending meeting invitations, clarifying 
		questions outside of customer meetings and other inquiries to the customer. 
		The customer contact works as a single-point two-way communicator, to reduce 
		amount of communication points. 

	\item[Advisor Contact] The advisor contact is responsible of all contact with the advisor outside 
		of the advisor meetings. Including sending meeting invitations, clarifying 
		questions outside of advisor meetings and other inquiries to the advisor. Advisor 
		contact works as a single-point two-way communicator, to reduce amount of 
		communication points.

	\item[Document Owner] The Document owner is responsible of finding a suitable tool for writing the report 
		in \LaTeX, and finding solutions with problems regarding \LaTeX. The document owner is also responsible for making sure all the correct 
		documents is added to the report, and will let the group know if something is missing. 

	\item[Secretary]
		Secretary is responsible for taking notes during all internal, 
		customer and advisor meetings. Meeting reports should meet a specific standard, 
		given by the project compendium. It is the responsibility of the meeting 
		report master to ensure this standard is followed.

	\item[Karotz Developer]
		The robot bunny, named Karotz, has an API for implementing features for controlling 
		the robot with an application. 
		The Karotz developer is responsible for developing the Karotz specific part of the system. 

	\item[Database manager]
		The database manager is responsible for selecting a suitable database tool for 
		the applications. The role also includes the responsibility of managing the 
		database architecture and connections towards the database.

	\item[System architect]
		The system architect is responsible of the overall architecture of the source code. 
		The architect has final vote in decisions regarding architecture specific problems. 

	\item[Quality assurance manager]
		The quality assurance manager has the overall responsibility for the applications and reports quality.

\end{description}
